---
title: 'Data Analysis of the Study "Comparison of prodigies & professional musicians"'
author: "VP"
date: "2022-01-05"
output: 
  html_document: 
    toc: yes
---

```{r setup, include = FALSE}
rm(list = ls())

library(pROC)
library(data.table)
library(magrittr)
library(psych)
library(ggplot2)
library(effsize)
library(Rmisc)
library(broom)
library(ggpubr)
library(tidyverse)
library(gridExtra)
library(qgraph)
library(lm.beta)
library(RColorBrewer)
library(stargazer)
library(car)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE)

source("functions.R")
dir.create("plots")

my_theme <- theme(
  panel.grid       = element_blank(),
  axis.line        = element_line(color = "black"),
  panel.background = element_rect(fill  = "white", colour = NA),
  axis.title.x     = element_text(
                       size = 12, 
                       vjust = -1
                     ),
  axis.title.y     = element_text(size = 12)
)
```
This document shows the data analysis used for our paper:

> You *Can* Tell a Prodigy From a Professional Musician: 
A Replication of Comeau et al.’s (2017) Study

submitted for publication in *Music Psychology*. We also provide a JASP file with any other analyses.

```{r DATA_prtcpnt import}
DATA_prtcpnt <- fread(
  "data/DATA_prtcpnt.csv",
  sep = ",", 
  encoding = "UTF-8",
  header = TRUE
) 

DATA_prtcpnt <- DATA_prtcpnt %>% 
  mutate(
    across(
      matches("Quiz[1-9]"), factor, levels = 1:5),
    across(
      c(
        Language,
        Retest_prodigy_Yes1No0,
        Retest_adult_Yes1No0,
        Pianist,
        HALT_Headphones1_Loudspeakers2,
        HALT_MonoStereo,
        HALT_Stereo1_MonoOrWrong2,
        Gender,
        MusicalProfession,
        PianistAndMusiciansGroups
      ) |
      matches("RatingCorrectStim|RatingAsProdigyStim"),
      factor
    ),
    Gender = fct_recode(
      Gender,
        "female"        = "1",
        "male"          = "2",
        "diverse"       = "3",
        "not specified" = "4"
    ),
    MusicalProfession = fct_recode(
      MusicalProfession,
      "Nonmusician"                           = "1",
      "Amateur musician"                       = "2",
      "Professional musician"                  = "5",
      "Other (specified in the next variable)" = "6"
    ),
    Pianist = fct_recode(
      Pianist,
      "Nonmusician"             = "0",
      "Musician, but no pianist" = "1",
      "Amateur pianist"          = "2",
      "Professional pianist"     = "4"
    ) 
  ) 
```

# Dataset 
*N* = `r nrow(DATA_prtcpnt)`

Levels of factor variables: 
```{r Levels of factor variables, warning = FALSE}
sapply(DATA_prtcpnt %>% select(where(is.factor)), levels)
```

```{r stimuli data stimuli import}
DATA_stimuli <- fread(
  "data/DATA_stimuli.csv", 
  sep = ",", 
  stringsAsFactors = TRUE
)

group.colors <- c(
  "Chopin_op10_5" = "#8DA0CB", 
  "LvB_op27_2_Mvt.1" = "#E78AC3", 
  "LvB_op27_2_Mvt.3" = "#A6D854", 
  "Mozart Piano Conc. No. 23 KV 488 Mvt. 1-Pt. 1" = "#FFD92F", 
  "Mozart Piano Conc. No. 23 KV 488 Mvt. 1-Pt. 2" = "#E5C494",
  "adult" = "#66C2A5",
  "child" = "#FC8D62"
)

DATA_stimuli_pairs <- DATA_stimuli %>% 
  group_by(Piece) %>% 
  dplyr::summarise(
    across(
      c(
        Intensity_Mean_dB,
        Intensity_SD_dB,
        Tempo_Mean,
        Tempo_SD,
        Overall_correct_responses,
        JMLE
      ),
      mean,
      .names = "mean_{.col}"
    ),
    diff_Intensity_Mean_dB         = max(Intensity_Mean_dB) - min(Intensity_Mean_dB),
    diff_Intensity_SD_dB           = max(Intensity_SD_dB) - min(Intensity_SD_dB),
    diff_Tempo_Mean                = max(Tempo_Mean) - min(Tempo_Mean),
    diff_Tempo_SD                  = max(Tempo_SD)- min(Tempo_SD),
    diff_overall_correct_responses = max(Overall_correct_responses) - min(Overall_correct_responses)
  )

DATA_stimuli_pairs <- as.data.table(DATA_stimuli_pairs)
```

# Number and Proportion of Pianists
```{r pianist}
pianists <- round(prop.table(table(DATA_prtcpnt$Pianist)), 3) * 100
pianists <- as.data.table(pianists)
colnames(pianists) <- c("Piano Expertise", "Proportion (in %)")
knitr::kable(pianists, use.names = FALSE)
```

# Hits, False Alarms, and Overall Correct Responses
Contingency Table for Hits 
```{r hits}
table(DATA_prtcpnt$P_Hits)
```

Contingency Table for False Alarms
```{r false alarms}
table(DATA_prtcpnt$P_FAs)
```

We had to correct proportions of Hits and False Alarms 
`r sum(
  DATA_prtcpnt$P_Hits == 0 |
  DATA_prtcpnt$P_Hits == 1
) +
sum(
  DATA_prtcpnt$P_FAs  == 0 |  
  DATA_prtcpnt$P_FAs  == 1   
  )`
times, because the proportions were 0 or 1.


Proportion of overall correct responses
```{r correct responses overall}
DATA_prtcpnt <- cbind(
  DATA_prtcpnt[,1:P_FAs],
  Overall_correct_responses = (DATA_prtcpnt$P_Hits + 1 - DATA_prtcpnt$P_FAs)/2,
  DATA_prtcpnt[, Sensitivity_d:ncol(DATA_prtcpnt)]
)

knitr::kable(
  describe(DATA_prtcpnt[, .(
    P_Hits, 
    Misses = 1 - P_Hits, 
    "Correct rejections" = 1 - P_FAs, 
    P_FAs, 
    Overall_correct_responses
  )]*100,
  skew = FALSE, trim=.1),
  digits = 2
)
```

The confidence interval of P_Hits, P_FAs, and overall correct responses are:
```{r confidence interval of P_Hits P_FAs and overall correct responses, echo=FALSE}
DATA_prtcpnt %>% 
  transmute(
    P_Hits, 
    Misses = 1 - P_Hits,
    Correct_rejections = 1 - P_FAs,
    P_FAs, 
    Overall_correct_responses
  ) %>% 
  summarise(across(
    .cols = everything(),
    .fns = ~ list(round(CI(.x * 100)[c(3,1)], 2))
  )) %>% 
  unnest(cols = c(
    P_Hits, 
    Misses, 
    Correct_rejections, 
    P_FAs, 
    Overall_correct_responses
  )) %>% 
  data.table::transpose(keep.names = "95% CI for Proportion in % for") %>% 
  rename("Lower" = V1, "Upper" = V2)

lapply(DATA_prtcpnt[, c("P_Hits", "P_FAs", "Overall_correct_responses")]*100, function(x) round(CI(x)[c(3, 1)], 2))

DATA_prtcpnt %>% 
  transmute(
    P_Hits, 
    Misses = 1 - P_Hits,
    Correct_rejections = 1 - P_FAs,
    P_FAs, 
    Overall_correct_responses
  ) %>% 
  summarise(across(
    .cols = everything(),
    .fns = list(
      M  = ~ mean(.x * 100) %>% round(2),
      SD = ~ sd(.x * 100) %>% round(2)
    ),
    .names = "{.col}-{.fn}"
  ),
  ) %>% 
  data.table::transpose(keep.names = "Proportion") %>% 
  separate(col = Proportion, into = c("Proportion", "Statistic"), sep = "-") %>% 
  tidyr::pivot_wider(Proportion, names_from = "Statistic", values_from = "V1") %>% 
  mutate(
    SE    = (SD/sqrt(nrow(DATA_prtcpnt))) %>% round(2),
    CI_LL = (M - 1.96*SE) %>% round(2),
    CI_UL = (M + 1.96*SE) %>% round(2)
  )

```

```{r correct responses subgroups}
DATA_prtcpnt %>% 
  mutate(PianistAndMusiciansGroups = "Overall") %>% 
  rbind(DATA_prtcpnt) %>% 
  group_by(
    "Level of Expertise" = fct_recode(
      PianistAndMusiciansGroups, 
      "Professional pianists" = "A",
      "Other professional musicians" = "B",
      "Amateur pianists" = "C",
      "Other amateur musicians" = "D",
      "Nonmusicians" = "E"
    ) %>% 
      fct_shift()
    ) %>% 
  rbind(
    DATA_prtcpnt %>% mutate(
      "Level of Expertise" = if_else(
        PianistAndMusiciansGroups != "E", 
        "Musicians", 
        "Nonmusicians (Hypothesis B)"
      ) %>% as_factor()
    )
  ) %>% 
  rbind(
    DATA_prtcpnt %>% mutate(
      "Level of Expertise" = if_else(
        PianistAndMusiciansGroups == "A", 
        "Pianists", 
        "Other"
      ) %>% factor(levels = c("Pianists", "Other"))
    )
  ) %>% 
  mutate( # Convert decimal number to percent
    Overall_correct_responses = Overall_correct_responses * 100
  ) %>%
  dplyr::summarise(
    n                     = n(),
    "%"                   = n()/nrow(DATA_prtcpnt) * 100,
    "M (Sensitivity d')"  = mean(Sensitivity_d),
    "SD (Sensitivity d')" = sd(Sensitivity_d),
    "SE (Sensitivity d')" = `SD (Sensitivity d')`/sqrt(n),
    "LL (Sensitivity d')" = `M (Sensitivity d')` - qt(.975, (n - 1))*`SD (Sensitivity d')`/sqrt(n()),                                     
    "UL (Sensitivity d')" = `M (Sensitivity d')` + qt(.975, (n - 1))*`SD (Sensitivity d')`/sqrt(n()),
    "M (% correct)"       = mean(Overall_correct_responses),
    "SD (% correct)"      = sd(Overall_correct_responses),
    "SE (% correct)"      = `SD (% correct)`/sqrt(n)
  ) %>% 
  mutate(
    across("%", round, 1),
    across(c("M (Sensitivity d')", "SD (Sensitivity d')", "SE (Sensitivity d')", `M (% correct)`, `SD (% correct)`), round, 2),
    across(c( "LL (Sensitivity d')", "UL (Sensitivity d')"), round, 3)
  ) %>% 
  knitr::kable()
```

# Sensitivity *d'*
## Descriptive Statistics
```{r sensitivity descriptive statistics}
knitr::kable(describe(DATA_prtcpnt[, .(Sensitivity_d)]), digits = 3)
```

The confidence interval of AUC is:
[`r round(CI(DATA_prtcpnt$Sensitivity_d)[c(3, 1)], 2)`].

## Sensitivity *d'* of Different Groups
```{r}
summary_sensitivity_d <- DATA_prtcpnt %>% 
  group_by(
    "Level of Expertise" = fct_recode(
      PianistAndMusiciansGroups, 
      !!!c(
        "Professional pianists" = "A",
        "Other professional musicians" = "B",
        "Amateur pianists" = "C",
        "Other amateur musicians" = "D",
        "Nonmusicians" = "E"
      )
    )
  ) %>%
  dplyr::summarise(
    n = n(), 
    Mean = mean(Sensitivity_d, na.rm = TRUE),
    SD = sd(Sensitivity_d, na.rm = TRUE),
    LL = Mean - qt(.975, (n - 1))*SD/sqrt(n()),                                             
    UL = Mean + qt(.975, (n - 1))*SD/sqrt(n())                                                    )

summary_sensitivity_d %>% 
  mutate(
    "Level of Expertise" = sapply(
      paste0(str_replace_all(`Level of Expertise`, " ", "\n"), "\n(n = ", n, ")"), 
      function(x) factor(x, levels = x)
    )
  ) %>% 
  ggplot(aes(y = Mean, x = `Level of Expertise`)) + 
    geom_point() + 
    geom_errorbar(aes(ymin = LL, ymax = UL), width = 0.2) + 
    scale_y_continuous(breaks = -1:7/10) +
    labs(y = expression(paste("Sensitivity ", italic("d'")))) +
    theme_bw()
```

## T-test and Cohens'd
```{r sensitivity t-Test and Cohens d}
t.test(
  DATA_prtcpnt$Sensitivity_d, 
  mu = 0, # chance level
  alternative = "two.sided" 
)

effsize::cohen.d(
  DATA_prtcpnt$Sensitivity_d, 
  f = NA,
  mu = 0
)
```

# Bias *c*
## Descriptive Statistics
```{r bias c descriptive statistics}
knitr::kable(describe(DATA_prtcpnt[, .(Bias_c)]), digits = 3)
```

The confidence interval of AUC is:
[`r round(CI(DATA_prtcpnt$Bias_c)[c(3, 1)], 2)`].

# AUC and ROC for Each Participant
## Calculation of ROC and AUC
We plot the receiver operating characteristic (ROC) curve of every twentieth participant.
```{r AUC and ROC for each participant, message = FALSE, warning = FALSE}
DATA_prtcpnt$AUC  <- 9999
plot_list <- list()
response  <- rep(c("prodigy", "adult"), 5) # 1 = case = prodigy; 0 = control = adult 
levels <- c("adult", "prodigy") # the value of the response for controls and cases, respectively

for (i in 1:nrow(DATA_prtcpnt)){
  DATA_prtcpnt[i, "AUC"] <- auc(
    response  = response, # 1 = case = Wunderkind; 0 = control = Erwachsener 
    predictor = as.numeric(DATA_prtcpnt[i, RatingStim01:RatingStim10]), 
    direction = ">", # control = adults = c(5, 6, 7, 8) > c(1, 2, 3, 4) = prodigy = case 
    levels    = levels
  )
  
  if (i%%20 == 0){ # Plot every 20th ROC curve
    plot_list[[i/20]] <- roc(
      response  = response, # 1 = case = prodigy; 0 = control = adult 
      predictor = as.numeric(DATA_prtcpnt[i, RatingStim01:RatingStim10]), 
      direction = ">", 
      percent   = TRUE, 
      plot      = TRUE, 
      ci        = TRUE
    ) 
  }
}
```

## Descriptive Statistics of AUC
`r knitr::kable(describe(DATA_prtcpnt$AUC), digits = c(0, 0, 2, 2, 2, 2, 2, 2, 2, 2, 3, 2, 3))`

The confidence interval of AUC is:
[`r round(CI(DATA_prtcpnt$AUC)[c(3, 1)], 2)`].


## t-Test and Cohen's d
Is Mean AUC (`r round(mean(DATA_prtcpnt$AUC), 3)`) significantly greater than chance level (0.5)? How large is this effect?
```{r t-test}
t.test(
  DATA_prtcpnt$AUC, 
  mu = 0.5, # chance level
  alternative = "greater" 
)

effsize::cohen.d(
  DATA_prtcpnt$AUC, 
  f = NA,
  mu = 0.5
)
```

# Histograms of Sensitivity *d'*, Bias *c* and AUC:
```{r plot histogram with Sensitivity Bias and AUC}
plot_list <- list()

plot_list[[1]] <- plot_hist(
  variable = "Sensitivity_d",
  x_lab = expression(paste("Sensitivity ", italic("d'"))),
  title = "A",
  x_intercept = 0, # chance level
  x_intercept_2 = 0.13,
  print_binwidth = FALSE
)

plot_list[[2]] <- plot_hist(
  variable = "Bias_c",
  x_lab = expression(paste("Bias ", italic("c"))),
  title = "B",
  x_intercept = NULL,
  print_binwidth = FALSE
)

plot_list[[3]] <- plot_hist(
  variable = "AUC",
  x_lab = "AUC",
  title = "C",
  x_intercept = .5, # chance level
  print_binwidth = FALSE
)

plot <- grid.arrange(
  grobs = plot_list, 
  ncol = 3, 
  width = unit(c(2.25, 2.25, 2.25), c("cm"))
)

ggsave(
  plot = plot,
  "Histogramms_d_c_AUC_ggplot.png", 
  path = "plots",
  device = "png",
  width = 8.36,
  height = 4.24,
  units = "in"
)
```

# Musical Culture: German (D) and Traditional Chinese (C)
## Musical Culture and Categorization of Musicianship
Proportions of each group per language (in %)
```{r language and musicianship group}
groups <- table(DATA_prtcpnt[, .(PianistAndMusiciansGroups, Language)])

groups <- rbind(
  round(
    prop.table(groups, margin = 2),
    3
  ) * 100,
  Total = c(100, 100)
)

groups <- data.table(
  Expertise = c(
    "Professional pianists",
    "Other professional musicians",
    "Amateur pianists",
    "Other amateur musicians",
    "Nonmusicians",
    "Total"
  ),
  groups
)

knitr::kable(groups, use.names = FALSE)
```

## Musical Culture and Classification Performance
Descriptive statistics
```{r  Descriptive statistics}
# https://stackoverflow.com/questions/25389683/obtaining-separate-summary-statistics-by-categorical-variable-with-stargazer-pac

DATA_prtcpnt %>% 
  select(
    Sensitivity_d, 
    AUC, 
    Quiz_Score,
    Overall_correct_responses, 
    Language # = group
  ) %>% 
  split(. $Language) %>% 
  walk(~ stargazer(., type = "text"))
```

Does a difference exist between the two different sub-samples, i.e. the German (D) and Traditional Chinese (C) speaking participants? How large is the effect (Cohen's *d*)?
```{r t-tests sensitivity, AUC, and correct responses}
# https://community.rstudio.com/t/use-dplyr-to-do-grouped-t-tests-and-get-number-of-observations-simultanously/23561/2

# Levene-Test
DATA_prtcpnt[, c(
   "Sensitivity_d", 
   "AUC", 
   "Quiz_Score",
   "Overall_correct_responses",
   "GoldMSI_Score"
 )] %>% 
lapply(leveneTest, DATA_prtcpnt$Language)

# t-test
tab1 <- DATA_prtcpnt %>% 
  select(
    Sensitivity_d, 
    AUC, 
    Quiz_Score,
    Overall_correct_responses, 
    GoldMSI_Score,
    Language # = group
  ) %>% 
  gather(key = "variable", value = "value", -Language) %>% # variable = category
  group_by(variable, Language) %>% 
  nest() %>% 
  spread(key = Language, value = data) %>% 
  mutate(
    t_test = map2(
      C, 
      D, 
      ~{t.test(.x$value, .y$value) %>% tidy()} # Student's t-test: <, var.equal = TRUE>
    ),
    C = map(C, nrow),
    D = map(D, nrow)
  ) %>% 
  unnest(cols = c(t_test)) %>% 
  ungroup() %>%
  dplyr::rename(
    "n C" = C, 
    "n D" = D,
    Mean_Difference = estimate,
    value_C = estimate1,
    value_D = estimate2,
    t_value = statistic,
    df = parameter
  )

tab2 <- DATA_prtcpnt %>% 
  select(
    Sensitivity_d, 
    AUC, 
    Quiz_Score,
    Overall_correct_responses, 
    GoldMSI_Score,
    Language # = group
  ) %>% 
  group_by(Language) %>% 
  summarise(across(.fns = sd, .names = "{.col}")) %>% 
  data.table::transpose(keep.names = "variable", make.names = "Language") %>% 
  rename("SD C" = C, "SD D" = D)

tab3 <- DATA_prtcpnt %>% 
  select(
    Sensitivity_d, 
    AUC, 
    Quiz_Score,
    Overall_correct_responses, 
    GoldMSI_Score,
    Language # = group
  ) %>% 
  gather(key = "variable", value = "value", -Language) %>% # variable = category
  group_by(variable) %>%
  rstatix::cohens_d(
    value ~ Language,
    conf.level = .95
  ) %>%
  ungroup() %>% 
  select(-c(.y.,group1, group2, n1, n2))
 
t_test <- tab1 %>% 
  inner_join(tab2, by = "variable") %>% 
  inner_join(tab3, by = "variable") %>% 
  as.data.table()

setorder(t_test[, .n := order(c(5, 1, 2, 3, 4))], .n)[, .n := NULL]

knitr::kable(t_test[, 
  .(
    variable, 
    `n C`,
    `n D`,
    "Mean Difference" = round(Mean_Difference, 3),
    "Mean C"          = round(value_C, 3),
    "Mean D"          = round(value_D, 3),
    "SD C"            = round(`SD C`, 3),
    "SD D"            = round(`SD D`, 3),
    "t"               = round(t_value, 2), 
    "p"               = round(p.value, 3), 
    df                = round(df, 0),
    Method            = method,
    "Effect size"     = round(effsize, 3),
    "Magnitude"       = magnitude
  )
])
```

# Analysis of Gold-MSI Subscale Perceptual Abilities

We collected data for the general factor of the Gold-MSI, which only comprises two items of the perceptual abilities subscale:  Items MS11_12 ("Ich kann zwei Interpretationen oder Versionen desselben Musikstücks miteinander vergleichen und über die Unterschiede diskutieren.") and MS11_23 ("Wenn ich singe, habe ich keine Ahnung, ob ich richtig oder falsch singe." (reversed). 

Is there a correlation (in the figures below: *R*) between Perceptual Abilities and Sensitivity *d'* or between Perceptual Abilities and AUC?
```{r Gold-MSI PA}
DATA_prtcpnt[, GMSI_PA_mean := (GoldMSI_ItemNo12 + GoldMSI_ItemNo23)/2]

cor.test(DATA_prtcpnt$GMSI_PA_mean, DATA_prtcpnt$Sensitivity_d)

(plot_gmsi_PA <- DATA_prtcpnt %>% 
  ggplot(
    aes(
      x = GMSI_PA_mean,
      y = Sensitivity_d
    )
  ) + 
  geom_jitter(
    alpha = 0.5,
    width = 0.05,
    height = 0,
    shape = 1
  ) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
  ) +
  stat_cor() +
  labs(
    x = "Mean of the two items of subscale Perceptual Abilities",
    y = expression(paste("Sensitivity ", italic("d'")))
  ) +
  my_theme
)

ggsave(
  plot = plot_gmsi_PA,
  "Subscale_PA_vs_d.png", 
  path = "plots",
  device = "png"
)

cor.test(DATA_prtcpnt$GMSI_PA_mean, DATA_prtcpnt$AUC)

DATA_prtcpnt %>% 
  ggplot(
    aes(
      x = GMSI_PA_mean,
      y = AUC
    )
  ) + 
  geom_jitter(
    alpha = 0.5,
    width = 0.05,
    height = 0,
    shape = 1
  ) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
  ) +
  stat_cor() +
  labs(
    x = "Mean of the two items of subscale Perceptual Abilities",
    y = "Area Under Curve"
  ) +
  my_theme
```

# Analysis of the Stimuli
## Musical and Acoustic Features
```{r plot musical features}
plot_list <- list()

plot_list <- map2(
  .x = DATA_stimuli[, 
    .(
      Intensity_Mean_dB,
      Intensity_SD_dB,
      Tempo_Mean,
      Tempo_SD         
    )], 
  .y = c( # x_labs,
    "Mean Intensity",
    "SD of Intensity",
    "Mean Tempo",
    "SD of Tempo"
  ),
  .f = plot_feature, 
  legend_position = "none",
  group_colors = group.colors[1:5]
)

legend_piece <- cowplot::get_legend(
  plot_feature_only_piece(
    variable        = DATA_stimuli[["Tempo_SD"]], 
    label           = "SD of Tempo", 
    legend_position = "left",
    group_colors    = group.colors[1:5]
  )
)  

legend_category <- cowplot::get_legend(
  plot_feature_only_performer(
    variable        = DATA_stimuli[["Tempo_SD"]], 
    label           = "SD of Tempo", 
    legend_position = "left"
  )  
)

plot_list[[5]] <- legend_piece
plot_list[[6]] <- legend_category
  
lay <- matrix(1:6, ncol = 2, byrow = TRUE)

plot <- grid.arrange(
  grobs = plot_list, 
  layout_matrix = lay
)

ggsave(
  plot = plot,
  "Feature_Analysis_descriptive.png", 
  path = "plots",
  device = "png"
)
```

## Musical Features and Overall Correct Responses
Is there a relation between musical features and overall correct responses?
```{r plot musical features and Overall_correct_responses}
plot_list <- list() 

plot_list <- pmap(
  .l = list(
    c( # x_vars
      "Intensity_Mean_dB",
      "Intensity_SD_dB",
      "Tempo_Mean",
      "Tempo_SD"         
    ),
     c( # x_labs
      "Mean Intensity",
      "SD of Intensity",
      "Mean Tempo",
      "SD of Tempo"
    ),
    c(56, 8, 112, 22) # R_positions
  ),
  .f = function(x_var, x_lab, R_position){
    print(as.name(x_var))
    print(cor.test(
      DATA_stimuli[[x_var]],
      DATA_stimuli[, c(Overall_correct_responses)]
    ))
    
    ggplot(
      data = DATA_stimuli,
      aes_string(
        x = x_var, 
        y = "Overall_correct_responses",
        color = "Piece"
      )
    ) +
      geom_point(aes(shape = Performer)) + # 16 or 20
      scale_colour_manual(values = group.colors) +
      stat_cor(
        aes(
          label = ..r.label..,
          color = Performer
        ),
        label.x = R_position
      ) +
      stat_cor(
        aes(
          label = ..r.label..,
          color = ""
        ),
        label.x = R_position,
        label.y = 42
      ) +
      guides(color = guide_legend(override.aes = list(size = 3))) +  
      geom_smooth(
        method = "lm", 
        formula = y ~ x,
        se = FALSE,
        color = "gray"
      ) +
      labs(x = x_lab, y = "Correct %", color= "Piece") +
      theme(legend.position  = "none") +
      my_theme
  }
)

plot_list[[5]] <- legend_piece
plot_list[[6]] <- legend_category

plot_list[[7]] <- cowplot::get_legend( # legend_performer
  plot_feature_performer_color(
    DATA_stimuli[["Tempo_SD"]], 
    "SD of Tempo", 
    legend_position = "left"
  )
) 

lay <- matrix(
  c(
    1, 1, 2, 2,
    3, 3, 4, 4,
    5, 5, 6, 7
  ),
  ncol = 4,
  byrow = TRUE
)


plot <- grid.arrange(
  grobs = plot_list, 
  layout_matrix = lay
)

ggsave(
  plot = plot,
  "Feature_Analysis_Percent_Correct.png", 
  path = "plots",
  device = "png"
)
```

##  Musical Features and Classification
```{r Classification}
DATA_stimuli <- DATA_stimuli %>% mutate(
  classification = case_when(
    (Performer == "adult" & Overall_correct_responses > 50) |  
    (Performer == "child" & Overall_correct_responses < 50) ~ "adult",
    (Performer == "child" & Overall_correct_responses > 50) |  
    (Performer == "adult" & Overall_correct_responses < 50) ~ "child")  
  )

plot_list <- list()

plot_list <- pmap(
  .l = list(
    x_var = DATA_stimuli[, 
      .(
        Intensity_Mean_dB,
        Intensity_SD_dB,
        Tempo_Mean,
        Tempo_SD         
      )], 
    x_lab = c( # x_labs,
      "Mean Intensity",
      "SD of Intensity",
      "Mean Tempo",
      "SD of Tempo"
    ),
    title = c("A", "B", "C", "D")
  ),
  .f = function(x_var, x_lab, title, ...) {
    ggplot(
      data = DATA_stimuli,
      aes_string(
        x = "classification", 
        y = x_var
      )
    ) +
      geom_boxplot() +
      geom_point(
        shape = 21, 
        aes(color = Performer),
        alpha = .75
      ) +
      labs(y = x_lab, x = "Classification") +
      ggtitle(title) +
      scale_colour_manual(values = group.colors[6:7]) +
      my_theme +
      theme(legend.position = "none")
  }
)
  
plot_list[[5]] <- cowplot::get_legend( # legend_performer
  plot_feature_performer_color(
    DATA_stimuli[["Tempo_SD"]], 
    "SD of Tempo", 
    legend_position = "top"
  )
) 

lay <- matrix(1:6, ncol = 2, byrow = TRUE)

plot <- grid.arrange(
  grobs = plot_list, 
  layout_matrix = lay
)

ggsave(
  plot = plot,
  "Boxplot_Classifications_Acoustical_Features.png", 
  path = "plots",
  device = "png",
  width = 11.8,
  height = 13.6,
  units = "cm"
)
```

## Regression
### Per Item
The variance of the overall correct response proportion is `r round(var(DATA_stimuli[, Overall_correct_responses]), 1)`, the mean is `r mean(DATA_stimuli[, Overall_correct_responses])`. We conducted a regression analysis to predict participant accuracy as measured by the overall percentage of correct responses using the acoustic features of the stimuli.
```{r regression per item}
formula <- 
  Overall_correct_responses ~ 
    Intensity_Mean_dB +
    Intensity_SD_dB +
    Tempo_Mean +
    Tempo_SD

model_item_level <- lm(
  formula = formula,
  data = DATA_stimuli
)

summary(model_item_level)

lm.beta(model_item_level)

DATA_stimuli[, prediction_overall_correct_resp := predict(model_item_level)]
```
$R^2$ is `r round(summary(model_item_level)$r.squared, 3)`.
The following plot shows the predicted values of the overall correct proportions:

```{r plot regression prediction}
(regression_plot <- ggplot(DATA_stimuli, aes(x = prediction_overall_correct_resp, y = Overall_correct_responses)) +
  geom_point() +
  geom_abline(color = "darkblue") +
  stat_cor(
    aes(label = ..rr.label..), 
    label.x = 45 
  ) +
  labs(
    x        = "Predicted Overall Correct Responses (in %)",
    y        = "Overall Correct Responses (in %)",
    title    = "Linear model prediction",
    subtitle = "Overall correct responses vs. predicted overall correct responses"
  ) +
  my_theme
)

ggsave(
  plot = regression_plot,
  "Feature_Analysis_Regression.png", 
  path = "plots",
  device = "png"
)
```

### Per Item Pair
Regression not possible, because *df* = 0.

#### Avg. Overall Correct Responses ~ Avg. Acoustic Feature, and Diff. Overall Correct Responses ~ Diff. Acoustic Feature
```{r regression on item pairs}
x_vars <- c(
  "mean_Intensity_Mean_dB",
  "mean_Intensity_SD_dB",
  "mean_Tempo_Mean",
  "mean_Tempo_SD", 
  "diff_Intensity_Mean_dB",
  "diff_Intensity_SD_dB",
  "diff_Tempo_Mean",
  "diff_Tempo_SD"         
)

y_vars <- c(
  "mean_Overall_correct_responses", 
  "diff_overall_correct_responses"
)

x_labs <- c(
  "Avg. Mean Intensity",
  "Avg. SD of Intensity",
  "Avg. Mean Tempo",
  "Avg. SD of Tempo",
  "\U0394 Mean Intensity", # \U0394 = Δ
  "\U0394 SD of Intensity",
  "\U0394 Mean Tempo",
  "\U0394 SD of Tempo"
)

y_labs <- c(
  "Avg. correct %",
  "\U0394 correct %" 
)

R_x_position <- c(
  62, 6.7, 112, 31,
  4.8, 0.5, 5, 11
)

R_y_position <- c(
  63, 63, 63, 63,
  13, 13, 13, 13
)

plot_list <- list() 
i <- 1

for (x_var in seq_along(x_vars)) {
  plot_list[[i]] <- ggplot(
    data = DATA_stimuli_pairs,
    aes_string(
      x = x_vars[x_var], 
      y = y_vars[(i%/% 5) + 1]
    )
  ) +
  geom_point(shape = 16) + # 16 or 20
  geom_smooth(
    method = "lm", 
    formula = y ~ x,
    se = FALSE,
    color = "darkblue"
  ) +
  stat_cor(
    aes(label = ..r.label..), 
    label.x = R_x_position[i],
    label.y = R_y_position[i]
  ) +
  labs(x = x_labs[i], y = y_labs[(i%/% 5) + 1]) +
  theme(
    panel.grid       = element_blank(),
    axis.line        = element_line(color = "black"),
    panel.background = element_rect(fill  = "white", colour = NA),
    axis.title.x     = element_text(vjust = -1)
  )  
  i <- i + 1
}

plot <- grid.arrange(
  grobs = plot_list, 
  ncol = 4,
  width = unit(c(4.5, 4.5, 4.5, 4.5), c("cm"))
)

ggsave(
  plot = plot,
  "Feature_Analysis_Item_Pairs_4x2.png", 
  path = "plots",
  device = "png"
)
```


#### Avg. Overall Correct Responses ~ Diff. Acoustic Feature
```{r regression on item pairs Avg Overall Correct Responses vs Diff Acoustic Feature}
plot_list <- map2(
  .x = c( # x_vars
    "diff_Intensity_Mean_dB",
    "diff_Intensity_SD_dB",
    "diff_Tempo_Mean",
    "diff_Tempo_SD"         
  ),
  .y =  c( # x_labs
    "\U0394 Mean Intensity",
    "\U0394 SD of Intensity",
    "\U0394 Mean Tempo",
    "\U0394 SD of Tempo"
  ),
  function(x_var, x_lab) {
    print(as.name(x_var))
    print(cor.test(
      DATA_stimuli_pairs[[x_var]],
      DATA_stimuli_pairs[, c(mean_Overall_correct_responses)]
    ))
    
    ggplot(
      data = DATA_stimuli_pairs,
      aes_string(
        x = x_var, 
        y = "mean_Overall_correct_responses"
      )
    ) +
      geom_point(shape = 16) + # 16 or 20
      geom_smooth(
        method = "lm", 
        formula = y ~ x,
        se = FALSE,
        color = "darkblue"
      ) +
      stat_cor(
        aes(label = ..r.label..), 
        label.x = 2 
      ) +
      labs(x = x_lab, y = "Avg. correct %") +
      my_theme  
  }
)

plot <- grid.arrange(
  grobs = plot_list, 
  ncol = 2,
  width = unit(c(4,4,4,4), c("cm"))
)

ggsave(
  plot = plot,
  "Feature_Analysis_Item_Pairs_2x2.png", 
  path = "plots",
  device = "png"
)
```

## AUC on Item Level (per Pair)
AUC for the five item pairs
```{r AUC on item pair level, echo=FALSE, message=FALSE}
start <- which(colnames(DATA_prtcpnt) == "RatingStim01")
end   <- which(colnames(DATA_prtcpnt) == "RatingStim09")

# Setting directions: 
# “>”: if the predictor values for the control group are higher than the values of the case group 
# (controls > t >= cases). 
# “<”: if the predictor values for the control group are lower or equal than the values of the case group 
# (controls < t <= cases)
# case = prodigy; control = adult

levels <- c("adult", "prodigy") # the value of the response for controls and cases, respectively

DATA_stimuli_pairs <- DATA_stimuli_pairs[, 
  AUC := sapply(seq(start, end, 2), function(i) {
      auc(
        response  = factor(
          c( # 1 = case = prodigy; 0 = control = adult
            rep("prodigy", nrow(DATA_prtcpnt)), 
            rep("adult",   nrow(DATA_prtcpnt))
          ),
          levels = levels
        ),
        predictor = c(DATA_prtcpnt[[i]], DATA_prtcpnt[[i + 1]]), 
        direction = ">",
        levels = levels
      )
  })
]
```


```{r plot AUC on item pair level, message=FALSE}
ROC_curves <- lapply(seq(start, end, 2), function(i) {
  print(colnames(DATA_prtcpnt)[i])
  roc(
    response  = factor(
      c( # 1 = case = prodigy; 0 = control = adult
        rep("prodigy", nrow(DATA_prtcpnt)), 
        rep("adult",   nrow(DATA_prtcpnt))
      ),
      levels = levels
    ),
    predictor = c(DATA_prtcpnt[[i]], DATA_prtcpnt[[i + 1]]), 
    direction = ">", 
    percent   = TRUE, 
    plot      = TRUE, 
    ci        = TRUE,
    print.auc = TRUE
  ) 
})
```


The AUC values for each item pair are: `r knitr::kable(DATA_stimuli_pairs[, .(Piece, AUC = round(AUC, 2))])`

Manually plotting the AUC

```{r manually calculating AUC per item pair}
# https://acutecaretesting.org/en/articles/roc-curves-what-are-they-and-how-are-they-used
lapply(seq(start, end, 2), function(i) {
  ROC_data <- data.table(
    CaseNo = c(DATA_prtcpnt$CaseNo, DATA_prtcpnt$CaseNo), 
    response  = factor( # correct response
      c( # 1 = case = prodigy; 0 = control = adult
        rep("prodigy", nrow(DATA_prtcpnt)),
        rep("adult", nrow(DATA_prtcpnt))
      ),
      levels = c("prodigy", "adult")
    ),
    predictor = c(
      DATA_prtcpnt[[i]],    # response to prodigy stimuli
      DATA_prtcpnt[[i + 1]] # response to adult stimuli
    )
  )
  
  ROC_data <- ROC_data %>% 
    arrange(predictor)
  
  ROC_data <- ROC_data %>% 
    mutate(
      prodigy_stimulus = ifelse(ROC_data$response == "prodigy", 1, 0), # sick
      adult_stimulus   = ifelse(ROC_data$response == "adult", 1, 0),
      sum_prodigy      = cumsum(prodigy_stimulus), # Y (sum)
      sum_adult        = cumsum(adult_stimulus),   # N (sum)
      sens             = sum_prodigy/278,
      x                = sum_adult/278
    ) %>% 
    ggplot(aes(x = x, y = sens)) +
      geom_point() +
      geom_abline() +
      labs(
        x = "1 - specificity (false positive rate)", 
        y = "Sensitivity (true positive rate)"
      ) +
      my_theme
})
```

### AUC ~ Overall Proportion of Correct Responses 
```{r correlation AUC and correct responses, message=FALSE}
DATA_stimuli_pairs %>% 
  ggplot(aes(x = AUC, y = mean_Overall_correct_responses, color = Piece)) +
    geom_point() +
    stat_cor() +
    geom_smooth(
        method = "lm", 
        formula = y ~ x,
        se = FALSE,
        color = "gray"
    ) +
  scale_colour_manual(values = group.colors[1:5]) +
  labs(y = "Mean Overall Correct Responses") +
  theme(legend.position  = "none") +
  my_theme
```

### AUC ~ Diff. Acoustic Feature
Is there a correlation between AUC for each item pair and the difference between the two values of the acoustic features (one value for adult and one for prodigy)? 
```{r regression on item pairs AUC vs Diff Acoustic Feature}
plot_list <- list() 

plot_list <- pmap(
  .l = list(
    c( # x_vars
      "diff_Intensity_Mean_dB",
      "diff_Intensity_SD_dB",
      "diff_Tempo_Mean",
      "diff_Tempo_SD"      
    ), 
    c( # x_labs
      "\U0394 Mean Intensity",
      "\U0394 SD of Intensity",
      "\U0394 Mean Tempo",
      "\U0394 SD of Tempo"
    ), 
    c(7.5, 1, 5, 13) # R_positions
  ),
  .f = function(x_var, x_lab, R_position){
    print(as.name(x_var))
    print(cor.test(
      DATA_stimuli_pairs[[x_var]],
      DATA_stimuli_pairs[, c(AUC)]
    ))
    
    ggplot(
      data = DATA_stimuli_pairs,
      aes_string(
        x = x_var, 
        y = "AUC",
        color = "Piece"
      )
    ) +
    geom_point(shape = 16) + # 16 or 20
    scale_colour_manual(values = group.colors) +
    geom_smooth(
      method = "lm", 
      formula = y ~ x,
      se = FALSE,
      color = "gray"
    ) +
    stat_cor(
      aes(label = ..r.label.., color = ""), 
      label.x = R_position 
    ) +
    labs(x = x_lab, y = "AUC") +
    theme(legend.position  = "none") +
    my_theme  
   
  }
)

plot_list[[5]] <- legend_piece

plot <- grid.arrange(
  grobs = plot_list, 
  ncol = 2
)

ggsave(
  plot = plot,
  "Feature_Analysis_Item_Pairs_AUC.png", 
  path = "plots",
  device = "png"
)
```

# IRT Measures and Acoustic Features
Is there a relation between the IRT measure JMLE and tempo variability (*SD* of Tempo) or between JMLE and AUC?
## IRT and Tempo Variability
```{r plot JMLE and SD tempo}
plot <- ggplot(DATA_stimuli,
  aes(
    x = Tempo_SD, 
    y = JMLE,
    color = Piece,
    group = Performer
  )) +
  geom_point(
    aes(shape = Performer),
    size = 3
  ) +
  geom_smooth(
    aes(
      color = "",
      group = ""
    ),
    method = "lm",
    formula = y ~ x,
    se = FALSE,
    color = "gray"
  ) +
  stat_cor(
    aes(
      label = ..r.label..,
      color = "",
      group = ""
    ),
    label.x = 19
  ) +
  stat_cor(
    aes(
      label = ..p.label..,
      color = "",
      group = ""
    ),
    label.x = 35
  ) +
  labs(x = "Tempo (SD)", y = "JMLE (Mean)") +
  scale_colour_manual(values = group.colors[1:5]) +
  theme(legend.position  = "none") +
  my_theme

lay <- matrix(
  c(1, 1, 2, 3),
  ncol = 2
)

grid.arrange(
  grobs = list(
    plot, 
    legend_piece,
    legend_category
  ), 
  layout_matrix = lay
)
```

## IRT and AUC
```{r plot JMLE and AUC}
plot <- ggplot(DATA_stimuli_pairs,
  aes(
    x = AUC, 
    y = mean_JMLE,
    color = Piece
  )) +
  geom_point(
    size = 3
  ) +
  geom_smooth(
    aes(
      color = "",
      group = ""
    ),
    method = "lm",
    formula = y ~ x,
    se = FALSE,
    color = "gray"
  ) +
  stat_cor(
    aes(
      label = ..r.label..,
      color = "",
      group = ""
    ),
    label.x = .5
  ) +
  stat_cor(
    aes(
      label = ..p.label..,
      color = "",
      group = ""
    ),
    label.x = .6
  ) +
  labs(y = "JMLE (Mean)") +
  scale_colour_manual(values = group.colors[1:5]) +
  theme(legend.position  = "none") +
  my_theme

grid.arrange(
  grobs = list(
    plot, 
    legend_piece
  ), 
  ncol = 2
)
```
